% The main file for developing the proposal. 
% Variants with different class options are 
% - submit.tex (no draft stuff, no ednotes, no revision information)
% - public.tex (like submit.tex, but no financials either) 
\providecommand{\classoptions}{,keys,general} % to be overwritten in variants
\documentclass[    % the options control the appearance, see the documentation
    gitinfo,       % show GIT information 
    noworkareas,   % do not generate work areas, this is a simple proposal
    RAM,           % also manage research assistant (HiWi) months
    general,       % make a title page, etc. 
    \classoptions] % the other class options from above, they can be overwritten e.g. in submit/final,tex
    {dfgproposal}
\addbibresource{../lib/dummy.bib}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[scaled=.90]{helvet}
\usepackage[utf8]{inputenc}

\begin{document}

\begin{center}\color{red}\huge
  This mock proposal is just an example for \texttt{dfgproposal.cls} it reflects the 
  current DFG template valid from October 2011.
\end{center}

%\urldef{\mikopubs}\url{http://kwarc.info/kohlhase/publications.html}
\begin{proposal}[
  PI=miko,
  mikoname=Michael Kohlhase,
  mikoaffiliation=FAU Erlangen N\"urnberg,
  mikodept=Computer Science,
  mikotitle=Prof. Dr., 
  pubspage=mikopubs,
  thema=Intelligentes Schreiben von Antr\"agen,
  acronym={iPoWr},
  acrolong={\underline{I}ntelligent} {\underline{P}r\underline{o}posal} {\underline{Wr}iting},
  title=\pn: \protect\pnlong,
  totalduration=3 years,
  start=1. Feb. 2010,
  months=24,
  RM=36,RAM=36,
  discipline=Computer Science, 
  areas=Knowledge Management,
  keywords={LaTeX Active Documents}]

  % It is often good to separate the top-level sections into separate files. 
% Especially in collaborative proposals. We do this here. And this allows us to share the
% state of the art of another proposal.
\input{../proposal/zusammenfassung}
\input{../proposal/summary}

\section*{Project Description -- Project Proposals}

\textbf{[First name last name, city of all applicants]}

\noindent\textbf{[Project title]}

\noindent\rule{\textwidth}{.5pt}

\subsection*{Project Description}

\begin{todo}{from the proposal guidelines}
	Your project description must not exceed 25 pages in total (up to \textbf{15 pages for sections 1 through 4} and up to \textbf{10 pages as of section 5}). The template formatting must be retained. In particular, the font should not be smaller thatn Arial 11 point, with line spacing no less than 1.2. For the sections \emph{Project-Related Publications and Bibliography}, the font should not be smaller than Arial 9 point.
\end{todo}

\input{../proposal/state}
\input{workplan}

\section{Bibliography concerning the state of the art, the research objectives, and the
  work programme \deu{(Literaturverzeichnis zum Stand der Forschung, zu den Zielen und dem
    Arbeitsprogramm)}}

\begin{todo}{from the proposal template}
  In this bibliography, list \textbf{only} the works you \textbf{cite} in your presentation of the state of
  the art, the research objectives, and the work programme. This bibliography is not the
  list of publications. Non-published works must be included with the proposal.
\end{todo}
\printbibliography[heading=empty]
% the following will not become part of the public proposal after all most of this is
% technical or confidential.
\ifpublic\else

\section{Relevance of sex, gender and/or diversity}

\begin{todo}{from the proposal template}
	Where applicable, please describe whether and to what extent the sex and/or gender
	\begin{itemize}
		\item of researchers
		\item of persons under study
		\item of individuals affected by the implementation of research results
		\item of animals under study
		\item with regard to samples taken from humans or animals
		\item in other respects
	\end{itemize}
	is relevant to the research project (methods, work programme, objectives, etc.).
	
	Where applicable, please also describe whether and to what extent diversity in terms of, for example, the state of health, ethnic background or culture of
	\begin{itemize}
		\item researchers
		\item persons under study
		\item individuals affected by the implementation of research results
		\item or diversity in other respects
	\end{itemize}
	may be significant for the research project (methods, work programme, objectives, etc.). Please explain to what extent these or similar considerations may also be relevant to animals under study or samples taken from humans or animals.
	
	Additional information is available at
	
	\url{www.dfg.de/diversity_dimensions}
\end{todo}

\pagebreak
\setcounter{page}{1}

\input{supplementary}
\input{../proposal/funds}

\section{Additional information \deu{(Ergänzende Erklärungen)}}

Funding proposal XYZ-83282 has been submitted prior to this proposal on related topic XYZ.
\fi %ifpublic
\end{proposal}

\end{document}
 
%%% Local Variables: 
%%% mode: LaTeX
%%% TeX-PDF-mode:t
%%% TeX-master: t
%%% End: 

% LocalWords:  empty bibflorian systems rabe institutions modal historical pub
% LocalWords:  kwarc till formalsafe miko gc ipower ipowerlong Antr agen Beitr

% LocalWords:  acrolong intellegible kollaboratives koh arenten ussen Proze pcg
% LocalWords:  Versionsmanagementsystem textsc unterst utzt konzentieren stex
% LocalWords:  mechanik workplan thispagestyle newpage Principcal cvpubsmiko pn
% LocalWords:  ourpubs zusammenfassung printbibliography pubspage ntelligent
% LocalWords:  iting pnlong
