% The main file for developing the proposal. 
% Variants with different class options are 
% - submit.tex (no draft stuff, no ednotes, no revision information)
% - public.tex (like submit.tex, but no financials either) 
\providecommand{\classoptions}{,keys} % to be overwritten in variants
\documentclass[    % the options control the appearance, see the documentation
    gitinfo,       % show GIT information 
    RAM,           % also manage research assistant (HiWi) months
    general,       % make a title page, etc. 
    \classoptions] % the other class options from above, they can be overwritten e.g. in submit/final,tex
    {dfgproposal}
\addbibresource{../lib/dummy.bib}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[scaled=.90]{helvet}
\usepackage[utf8]{inputenc}

\begin{document}
\begin{center}\color{red}\huge
  This mock proposal is an example for \texttt{dfgproposal.cls} it reflects the current
  DFG template from 2012.
\end{center}
\begin{Large}\color{red}
  The first time this proposal file is being run it will throw errors (forward references
  need to be initialized), just run pdflatex on it again.
\end{Large}

% \urldef{\gcpubs}\url{http://www.pcg.phony/~gc/pubs.html}
% \urldef{\mikopubs}\url{http://kwarc.info/kohlhase/publications.html}
\begin{proposal}[
  PI=miko,
  mikoname=Michael Kohlhase,
  mikoaffiliation=FAU Erlangen N\"urnberg,
  mikodept=Computer Science,
  mikotitle=Prof. Dr.,
  PI=gc,
  gcname=Great Communicator,
  gcaffiliation=Power Consulting GmbH,
  gcdept=Science Affairs,
  gctitle=Dr.,
  site=fau,
  fauacronym=FAU,
  faushortname=FAU Erlangen N\"urnberg,
  site=pcg,
  pcgacronym=PCG,
  pcgshortname=Power Consulting GmbH,
  thema=Intelligentes Schreiben von Antr\"agen,
  acronym={iPoWr},
  acrolong={\underline{I}ntelligent} {\underline{P}r\underline{o}posal} {\underline{Wr}iting},
  title=\pn: \protect\pnlong,
  totalduration=3 years,
  start=1. Feb. 2010,
  months=24,
%  pcgRM=36, pcgRAM=36, fauRM=36, fauRAM=36,
  discipline=Computer Science, 
  areas=Knowledge Management,
  keywords={LaTeX Active Documents}
  ]

% It is often good to separate the top-level sections into separate files. 
% Especially in collaborative proposals. We do this here. 
\input{zusammenfassung}
\input{summary}
\input{state}
\input{workplan}

\section{Bibliography Concerning the State of the Art, the Research objectives, and the
  Work Programme}\label{sec:bib}

\begin{todo}{from the proposal template}
In this bibliography, list only the works you cite in your presentation of the state of the
art, the research objectives, and the work programme. This bibliography is not the list
of publications. Non-published works must be included with the proposal.
\end{todo}
\printbibliography[heading=empty,notcategory=featured]
% the following will not become part of the public proposal after all most of this is
% technical or confidential.
\ifpublic\else
\input{funds}
\input{preconditions}

\section{Additional Information}\label{sec:additional}

Funding proposal XYZ-83282 has been submitted prior to this proposal on related topic XYZ.
\fi % ifpublic
\end{proposal}
\end{document}
 
%%% Local Variables: 
%%% mode: LaTeX
%%% TeX-PDF-mode:t
%%% TeX-master: t
%%% End: 

% LocalWords:  empty bibflorian systems rabe institutions modal historical pub ednotes
% LocalWords:  kwarc till formalsafe miko gc ipower ipowerlong Antr agen Beitr gcpubs

% LocalWords:  acrolong intellegible kollaboratives koh arenten ussen Proze pcg miko,PI
% LocalWords:  Versionsmanagementsystem textsc unterst utzt konzentieren stex
% LocalWords:  mechanik workplan thispagestyle newpage Principcal cvpubsmiko pn
% LocalWords:  ourpubs zusammenfassung printbibliography pubspage ntelligent
% LocalWords:  iting pnlong dfgproposal.cls
